Graphs for 1000  Generations

### 2021-07-05 graphs_newt_snakes/fig_1000.Rmd
fixed error in trasforming and added a phenotype changing graph to see how phenotpes were changing over 1000 gens. the one for 2 sims is not working yet

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(viridis)
#setwd("~/Desktop/Proposal Old Drafts")
```

## This is a r file to show what the phenotypess are after 1000 generations
A problem that I have been experiencing is that the phenotypes seem so go wild really quickly

@@

Lets just visualize what the phenotypes are doing

@@

# Mistake Simulations 
I tried to run SLiM simulation different with the selected parameters and the MSprime   both_su_1e-10_nu_1e-10_sue_0.01_nue_0.01 (s/n u mutation rate, n/s ue mutation effect size).
However I flipped the mutation rate and effect size. So... new experiment with really large mutation rate????

@@

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_1)+
  scale_y_log10(limits=c(true_min_1+0.8, true_max_1))+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  ggtitle("Phenotype Measurements for Newts and Snakes") +
  xlab("Generation") + ylab("Average Phenotypes")+
  theme_bw()

@@

## need to work on making this figure better 
files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(min_difference, max_difference)+
  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
  #scale_y_log10()+
  #scale_y_log10(limits=c(min_difference_1, max_difference_1))+
  geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
    ggtitle("Difference Between Phenotypes (Snakes-Newts)") +
  xlab("Generation") + ylab("Average Difference")+
  theme_bw()

@@

@@

I want to see what the un-transformed phentypes are and compare them to their transformed buddies to figure out what values I should be using for sigma and

@@

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=Newt_mean_Pheno)) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = exp(Newt_mean_Pheno/10)), color = "darkred") + 
  ggtitle("Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()
q <- ggplot(file1, aes(x=Snake_mean_Pheno)) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = exp(Snake_mean_Pheno/10)), color = "darkred") + 
  ggtitle("Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()

@@

  file <- read.table(current_file, header = TRUE)
 p <- p + geom_line(data=file, aes(y = exp(Newt_mean_Pheno/10)), color = "darkred")

 q <- q + geom_line(data=file, aes(y = exp(Snake_mean_Pheno/10)), color="steelblue", linetype="twodash")
}

@@

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_2)+
  scale_y_log10(limits=c(true_min_2+0.5, true_max_2))+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  ggtitle("Phenotype Measurements for Newts and Snakes") +
  xlab("Generation") + ylab("Average Phenotypes")+
  theme_bw()

@@

p 
```
```{r data from multiple msprime, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  ylim(min_difference_2, max_difference_2)+
  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
  #scale_y_log10()+
  #scale_y_log10(limits=c(min_difference_2, max_difference_2))+
  geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
    ggtitle("Difference Between Phenotypes (Snakes-Newts)") +
  xlab("Generation") + ylab("Average Difference")+
  theme_bw()

@@

@@

I want to see what the un-transformed phentypes are and compare them to their transformed buddies to figure out what values I should be using for sigma and

@@

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=Newt_mean_Pheno)) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = exp(Newt_mean_Pheno/10)), color = "darkred") + 
  ggtitle("Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()
q <- ggplot(file1, aes(x=Snake_mean_Pheno)) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = exp(Snake_mean_Pheno/10)), color = "darkred") + 
  ggtitle("Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()

@@

# Expanded Experiment 
This time I examine what the SLIM script would generate is both the MSprime and SLIM are ran with the variables that I picked. I ran 144 SLiM simulations & MSprime with different parameters values.

@@

files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_3)+
  #scale_y_continuous(trans=log10_trans(), limits=c(0,true_max_3))+
  #scale_y_log10()+
  scale_y_log10(limits=c(0.001,true_max_3))+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  ggtitle("Phenotype Measurements for Newts and Snakes") +
  xlab("Generation") + ylab("Average Phenotypes")+
  theme_bw()

@@

Some other things that might be goo to look at:

The difference between the average phenotypes

@@

files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(min_difference, max_difference)+
  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
  #scale_y_log10()+
  scale_y_log10(limits=c(min_difference_3, max_difference_3))+
  geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
  ggtitle("Difference Between Phenotypes (Snakes-Newts)") +
  xlab("Generation") + ylab("Average Difference")+
  theme_bw()

@@

@@

files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=Newt_mean_Pheno)) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = exp(Newt_mean_Pheno/10)), color = "darkred") + 
  ggtitle("Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()
q <- ggplot(file1, aes(x=Snake_mean_Pheno)) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = exp(Snake_mean_Pheno/10)), color = "darkred") + 
  ggtitle("Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()

for (current_file in files){
  #print(current_file)
   file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  file <- file[complete.cases(file), ]
  #print(file$Newt_mean_Pheno)
  #print(exp(file$Newt_mean_Pheno/10))
  file <- read.table(current_file, header = TRUE)
 p <- p + geom_line(data=file, aes(y = exp(as.numeric(Newt_mean_Pheno)/10)), color = "darkred")

 q <- q + geom_line(data=file, aes(y = exp(as.numeric(Snake_mean_Pheno)/10)), color="steelblue", linetype="twodash")
}

#p 
#q

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(viridis)
library(colorspace)
#setwd("~/Desktop/Proposal Old Drafts")
```

## This is a r file to show what the phenotypess are after 1000 generations
A problem that I have been experiencing is that the phenotypes seem so go wild really quickly. One species' phenotype balloons to be really high while the other species" phenotype stays really low.

@@

Lets just visualize what the phenotypes are doing.

@@

# Mistake Simulations 
I tried to run SLiM simulation different with the selected parameters and the MSprime   both_su_1e-10_nu_1e-10_sue_0.01_nue_0.01 (s/n u mutation rate, n/s ue mutation effect size).
However I flipped the mutation rate and effect size. So... new experiment with really large mutation rate and small effect size????

@@

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_1)+
  scale_y_log10(limits=c(true_min_1+0.8, true_max_1))+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  ggtitle("Wrong1sim: Phenotype Measurements for Newts and Snakes") +
  xlab("Generation") + ylab("Average Phenotypes")+
  theme_bw()

@@

## need to work on making this figure better 
files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(min_difference, max_difference)+
  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
  #scale_y_log10()+
  #scale_y_log10(limits=c(min_difference_1, max_difference_1))+
  geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
    ggtitle("Wrong1sim: Difference Between Phenotypes (Snakes-Newts)") +
  xlab("Generation") + ylab("Average Difference")+
  theme_bw()

@@

## How much did the phenotypes of newts and snakes change over 1000 generations

For this figure I want there to be 2 sets of points (4 complete points) for each simulation taking the first and last mean phenotype for the newt and the snake. Essentially, asking if the phenotypes of the newts and snakes changed over 1000 generations?

```{r pheno change, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=1:144)) +
  xlim(0, 145)+
  #ylim(newt_min_pheno_1, newt_max_pheno_1)+
  geom_point(aes(x = 1, y = Newt_mean_Pheno[1]), color = darken("darkred")) +
  geom_point(aes(x = 1, y = Newt_mean_Pheno[50]), color = lighten("darkred")) +
  geom_point(aes(x = 1, y = Snake_mean_Pheno[1]), color = darken("steelblue")) +
  geom_point(aes(x = 1, y = Snake_mean_Pheno[50]), color = lighten("steelblue")) +
  ggtitle("Wrong1sim: Phenotype Change") +
  xlab("Simulation number") + ylab("Phenotype")+
  theme_bw()
i=1
for (current_file in files){

  file <- read.table(current_file, header = TRUE)
 p <- p + geom_point(data= file, x = i, aes(y = Newt_mean_Pheno[1]), color = darken("darkred")) +
   geom_point(data= file,x = i, aes(y = Newt_mean_Pheno[50]), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = Snake_mean_Pheno[1]), color = darken("steelblue")) +
  geom_point(data= file, x = i, aes(y = Snake_mean_Pheno[50]), color = lighten("steelblue"))
 i = i+1
}

p

@@

I want to see what the un-transformed phentypes are and compare them to their transformed buddies to figure out what values I should be using for sigma and mu.

I calculated the phenotypes from this expression, newt pheno = exp(inds_n.sumOfMutationsOfType(m1)/10). So to un-transform and find the # of mutations I need to ln both sides of the equation ln(pheno=e^(sumOfMutations/10)). Then solve for sumOfMutations,  sumOfMutations = 10 * ln(pheno)

Notes:
difference in the trees betw two chromosomes in a pop of size N is 4N
so # of differing mutations is like 4 N L mu where L = genome length, mu = mutaiton rate per bp and if each mutation has an effect size that is N(0, sd=sigma), then the sum of K of these has mean 0 and SD= sigma * sqrt(K). So untransformed phenotypes (sum of effect sizes) should have mean 0 and SD= sigma * sqrt(4 N L mu). So, you'd work out what SD you want, then given mu solve for sigma (the SD of effect size)

@@

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=Newt_mean_Pheno)) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = (log(Newt_mean_Pheno)*10)), color = "darkred") + 
  ggtitle("Wrong1sim: Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()
q <- ggplot(file1, aes(x=Snake_mean_Pheno)) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = (log(Snake_mean_Pheno)*10)), color = "steelblue") + 
  ggtitle("Wrong1sim: Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()

@@

  file <- read.table(current_file, header = TRUE)
 p <- p + geom_line(data=file, aes(y = (log(Newt_mean_Pheno)*10)), color = "darkred")

 q <- q + geom_line(data=file, aes(y = (log(Snake_mean_Pheno)*10)), color="steelblue", linetype="twodash")
}

@@

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_2)+
  scale_y_log10(limits=c(true_min_2+0.5, true_max_2))+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  ggtitle("1sim: Phenotype Measurements for Newts and Snakes") +
  xlab("Generation") + ylab("Average Phenotypes")+
  theme_bw()

@@

```{r data from multiple msprime, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  ylim(min_difference_2, max_difference_2)+
  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
  #scale_y_log10()+
  #scale_y_log10(limits=c(min_difference_2, max_difference_2))+
  geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
    ggtitle("1sim: Difference Between Phenotypes (Snakes-Newts)") +
  xlab("Generation") + ylab("Average Difference")+
  theme_bw()

@@

p 
```
## How much did the phenotypes of newts and snakes change over 1000 generations

```{r 1sim pheno change, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=1:144)) +
  xlim(0, 145)+
  #ylim(newt_min_pheno_1, newt_max_pheno_1)+
  geom_point(aes(x = 1, y = Newt_mean_Pheno[1]), color = darken("darkred")) +
  geom_point(aes(x = 1, y = Newt_mean_Pheno[50]), color = lighten("darkred")) +
  geom_point(aes(x = 1, y = Snake_mean_Pheno[1]), color = darken("steelblue")) +
  geom_point(aes(x = 1, y = Snake_mean_Pheno[50]), color = lighten("steelblue")) +
  ggtitle("1sim: Phenotype Change") +
  xlab("Simulation number") + ylab("Phenotype")+
  theme_bw()
i=1
for (current_file in files){

  file <- read.table(current_file, header = TRUE)
 p <- p + geom_point(data= file, x = i, aes(y = Newt_mean_Pheno[1]), color = darken("darkred")) +
   geom_point(data= file,x = i, aes(y = Newt_mean_Pheno[50]), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = Snake_mean_Pheno[1]), color = darken("steelblue")) +
  geom_point(data= file, x = i, aes(y = Snake_mean_Pheno[50]), color = lighten("steelblue"))
 i = i+1
}

p

@@

@@

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=Newt_mean_Pheno)) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = (log(Newt_mean_Pheno)*10)), color = "darkred") + 
  ggtitle("1sim: Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()
q <- ggplot(file1, aes(x=Snake_mean_Pheno)) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = (log(Snake_mean_Pheno)*10)), color = "steelblue") + 
  ggtitle("1sim: Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()

@@

# Expanded Experiment 2sims: 
This time I examine what the SLIM script would generate is both the MSprime and SLIM are ran with the variables that I picked. I ran 144 SLiM simulations & MSprime with different parameters values.

@@

files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_3)+
  #scale_y_continuous(trans=log10_trans(), limits=c(0,true_max_3))+
  #scale_y_log10()+
  scale_y_log10(limits=c(0.001,true_max_3))+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  ggtitle("2sims: Phenotype Measurements for Newts and Snakes") +
  xlab("Generation") + ylab("Average Phenotypes")+
  theme_bw()

@@

## Difference between snake and newt pheotypes

@@

files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(min_difference, max_difference)+
  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
  #scale_y_log10()+
  scale_y_log10(limits=c(min_difference_3, max_difference_3))+
  geom_line(aes(y = Snake_mean_Pheno - Newt_mean_Pheno), color = "mediumseagreen") + 
  ggtitle("2sims: Difference Between Phenotypes (Snakes-Newts)") +
  xlab("Generation") + ylab("Average Difference")+
  theme_bw()

@@

p 
```
## How much did the phenotypes of newts and snakes change over 1000 generations

```{r 2sim pheno change, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=1:144)) +
  xlim(0, 145)+
  geom_point(aes(x = 1, y = as.numeric(Newt_mean_Pheno[1])), color = darken("darkred")) +
  geom_point(aes(x = 1, y = as.numeric(Newt_mean_Pheno[50])), color = lighten("darkred")) +
  geom_point(aes(x = 1, y = as.numeric(Snake_mean_Pheno[1])), color = darken("steelblue")) +
  geom_point(aes(x = 1, y = as.numeric(Snake_mean_Pheno[50])), color = lighten("steelblue")) +
  ggtitle("2sim: Phenotype Change") +
  xlab("Simulation number") + ylab("Phenotype")+
  theme_bw()
i=1
for (current_file in files){

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- 0
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- 0
  file <- file[complete.cases(file), ]
 p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])), color = darken("darkred")) +
   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])), color = darken("steelblue")) +
  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])), color = lighten("steelblue"))
 i = i+1
}

p

@@

files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=as.numeric(Newt_mean_Pheno))) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = (log(as.numeric(Newt_mean_Pheno))*10)), color = "darkred") + 
  ggtitle("2sims: Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()
q <- ggplot(file1, aes(x=as.numeric(Snake_mean_Pheno))) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = (log(as.numeric(Snake_mean_Pheno))*10)), color = "steelblue") + 
  ggtitle("2sims: Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()

for (current_file in files){
  #print(current_file)
  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  file <- file[complete.cases(file), ]
  #print(file$Newt_mean_Pheno)
  #print(exp(file$Newt_mean_Pheno/10))
  #print(log(as.numeric(file$Newt_mean_Pheno))*10)
  file <- read.table(current_file, header = TRUE)
 p <- p + geom_line(data=file, aes(y = (log(as.numeric(Newt_mean_Pheno))*10)), color = "darkred",na.rm = TRUE)

 q <- q + geom_line(data=file, aes(y = (log(as.numeric(Snake_mean_Pheno))*10)), color="steelblue", linetype="twodash", na.rm = FALSE)
}
